PDBF Testdokument

### 2015-03-12 beamer_test.tex
moved floating point calculation from latex to java because of performance reasons.

\mdqoff

\addtobeamertemplate{note page}{\setlength{\parskip}{12pt}}
\makeatletter
\beamertemplatenavigationsymbolsempty
\setbeamerfont{footline}{size=\normalsize}
\setbeamertemplate{footline}{{\par\hspace*{\fill}\vspace*{0.25cm}\insertframenumber~~~}}
\setbeamertemplate{items}[default]
\setbeamertemplate{sections/subsections in toc}[sections numbered]
\setbeamertemplate{subsection in toc}{}
\setbeamercolor{title}{fg=white,bg=red!50!green!70}
\setbeamercolor{frametitle}{fg=white,bg=red!50!green!70}
\setbeamercolor{subsection in toc}{fg=black}
\setbeamercolor{section in toc}{fg=black}
\setbeamercolor{item}{fg=black}
\makeatother

@@

\DBSQLText{CREATE TABLE table1 (column1 INTEGER, column2 DATE, column3 FLOAT);}
\DBSQLFile{somedb.sql}
\DBSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{testtest, pgtest}% , dim_time, dim_compiler, dim_dataset, dim_implementation, dim_layout, dim_query, dim_machine, fact_experiment

@@

\begin{frame}
\titlepage
\vspace{-2.3cm}
\begin{center}
\includegraphics[scale=0.25]{C:/Users/User/Downloads/UdS-Logo.jpg}
\end{center}
Presenter: Patrick Bender
\end{frame}
\note{bla}

\section{SQL Queries} 
\subsection*{}
\begin{frame}\frametitle{Simple Query}

\end{frame}
\note{bla}

\subsection*{}
\begin{frame}\frametitle{Advanced Query}

\end{frame}
\note{bla}

\section{Charts} 
\subsection*{}
\begin{frame}\frametitle{Line Chart with little data}
\def\test{testtest}
	{\centering
	\lineChart[width=0.4\textwidth, height=0.3\textwidth, xunit=\test Money (in €), yunit=Date, options={"title": "Title", "titleHeight": 25}]{SELECT * FROM data1;}%
	\\}
\end{frame}
\note{bla}

\subsection*{}
\begin{frame}\frametitle{Line Chart with much data}
	{\centering
	\lineChart[width=0.4\textwidth, height=0.4\textwidth, xunit=Number, yunit=Row ID]{SELECT Zahl1, Zahl2 as some_number FROM pgtest WHERE Zahl1 > 45000;}%
	\\}
\end{frame}
\note{bla}

\section*{}
\begin{frame}
	Thank you for your attention!
\end{frame}
\note{bla}

\begin{frame}
	Questions?
\end{frame}
\note{bla}

>>>>

\addtobeamertemplate{note page}{\setlength{\parskip}{12pt}}
\makeatletter
\beamertemplatenavigationsymbolsempty
\setbeamerfont{footline}{size=\normalsize}
\setbeamertemplate{footline}{{\par\vspace*{-2cm}\hspace*{\fill}\vspace*{0.25cm}\insertframenumber~~~}}
\setbeamertemplate{items}[default]
\setbeamertemplate{sections/subsections in toc}[sections numbered]
\setbeamertemplate{subsection in toc}{}
\setbeamercolor{title}{fg=white,bg=red!50!green!70}
\setbeamercolor{frametitle}{fg=white,bg=red!50!green!70}
\setbeamercolor{subsection in toc}{fg=black}
\setbeamercolor{section in toc}{fg=black}
\setbeamercolor{item}{fg=black}
\def\beamer@framenotesbegin{% at beginning of slide
  \gdef\beamer@noteitems{}%
  \gdef\beamer@notes{{}}% used to be totally empty.
}
\addtobeamertemplate{frametitle}{}{\vspace{0.4cm}}
\makeatother

@@

\DBSQLText{CREATE TABLE table1 (column1 INTEGER, column2 DATE, column3 FLOAT);}
\DBSQLFile{somedb.sql}
\DBSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{testtest, pgtest, dim_time, dim_compiler, dim_dataset, dim_implementation, dim_layout, dim_query, dim_machine, fact_experiment}%

@@

\begin{frame}
\vspace{-1.0cm}
\titlepage
\vspace{-2.5cm}
\begin{center}
\includegraphics[scale=0.25]{C:/Users/User/Downloads/UdS-Logo.jpg}
\end{center}
Presenter: Patrick Bender
\end{frame}
\note{bla}

\section{SQL Queries} 
\subsection*{}
\begin{frame}\frametitle{Simple Queries} 
	\sql{SELECT * FROM test;}\\[12pt]
	\sql{SELECT col2 FROM test WHERE col1=1;}\\[12pt]
	\sqlmult{INSERT INTO test}{INSERT INTO test VALUES (1, 123);}\\
	\sqlmult{VALUES (1, 123);}{INSERT INTO test VALUES (1, 123);}
\end{frame}
\note{bla}

\subsection*{}
\begin{frame}\frametitle{Advanced Queries}
\vspace{-0.4cm}
	\def\longquery{SELECT
m.cpu + ' (' +  m.cpuarchitecture + ')' AS Machine,
d.tableschema   AS [Table schema],
c.compiler      AS Compiler,
c.optlevel      AS [Opt. level],
COALESCE(cast(l.chunksize AS VARCHAR), 'n/a') AS [Chunk size (tuples)],
IIF(i.templateparam, 'Compile time', 'Runtime') AS [Chunk size provided at],
IIF(i.logscaleparam, 'Powers of 2', 'Multiples of 2') AS [Chunk sizes considered],
t.timestamp 	AS [Time of experiment],
ROUND(v.runtime, 3) 		AS [Query time (in Sec)]
FROM fact_experiment AS v
    JOIN dim_machine m ON m.id = v.machineid
    JOIN dim_dataset d ON d.id = v.datasetid
    JOIN dim_compiler c ON c.id = v.compilerid
    JOIN dim_layout l ON l.id = v.layoutid
    JOIN dim_implementation i ON i.id = v.implementationid
    JOIN dim_query q ON q.id = v.queryid
    JOIN dim_time t ON t.id = v.timeid
ORDER BY m.id DESC, d.tableschema, q.querytext,
    c.compiler, c.optlevel, i.templateparam, i.logscaleparam, l.chunksize
LIMIT 100;}
	\begin{scriptsize}
	\sqlmult{SELECT}{\longquery}\\
	\sqlmult{m.cpu + ' (' +  m.cpuarchitecture + ')' AS Machine,}{\longquery}\\
	\sqlmult{d.tableschema   AS [Table schema],}{\longquery}\\
	\sqlmult{c.compiler      AS Compiler,}{\longquery}\\
	\sqlmult{c.optlevel      AS [Opt. level],}{\longquery}\\
	\sqlmult{COALESCE(cast(l.chunksize AS VARCHAR), 'n/a') AS [Chunk size (tuples)],}{\longquery}\\
	\sqlmult{IIF(i.templateparam, 'Compile time', 'Runtime') AS [Chunk size provided at],}{\longquery}\\
	\sqlmult{IIF(i.logscaleparam, 'Powers of 2', 'Multiples of 2') AS [Chunk sizes considered],}{\longquery}\\
	\sqlmult{t.timestamp 	AS [Time of experiment],}{\longquery}\\
	\sqlmult{ROUND(v.runtime, 3) 		AS [Query time (in Sec)]}{\longquery}\\
	\sqlmult{FROM fact\_experiment AS v}{\longquery}\\
	\sqlmult{    JOIN dim\_machine m ON m.id = v.machineid}{\longquery}\\
	\sqlmult{    JOIN dim\_dataset d ON d.id = v.datasetid}{\longquery}\\
	\sqlmult{    JOIN dim\_compiler c ON c.id = v.compilerid}{\longquery}\\
	\sqlmult{    JOIN dim\_layout l ON l.id = v.layoutid}{\longquery}\\
	\sqlmult{    JOIN dim\_implementation i ON i.id = v.implementationid}{\longquery}\\
	\sqlmult{    JOIN dim\_query q ON q.id = v.queryid}{\longquery}\\
	\sqlmult{    JOIN dim\_time t ON t.id = v.timeid}{\longquery}\\
	\sqlmult{ORDER BY m.id DESC, d.tableschema, q.querytext,}{\longquery}\\
	\sqlmult{    c.compiler, c.optlevel, i.templateparam, i.logscaleparam, l.chunksize}{\longquery}\\
	\sqlmult{LIMIT 100;}{\longquery}\\
	\end{scriptsize}
\end{frame}
\note{bla}

\section{Charts} 
\subsection*{}
\begin{frame}\frametitle{Line Chart with little data}
	{\centering
	\lineChart[width=0.8\textwidth, height=0.6\textwidth, xunit=Money (in €), yunit=Date, options={"title": "Title", "titleHeight": 25}]{SELECT * FROM data1;}%
	\\}
\end{frame}
\note{bla}

\subsection*{}
\begin{frame}\frametitle{Line Chart with much data}
	{\centering
	\lineChart[width=0.8\textwidth, height=0.6\textwidth, xunit=Number, yunit=Row ID]{SELECT Zahl1, Zahl2 as some_number FROM pgtest WHERE Zahl1 > 45000;}%
	\\}
\end{frame}
\note{bla}

\section*{}
\begin{frame}
\vspace{1.0cm}
	\begin{center}Thank you for your attention!\end{center}
\end{frame}
\note{bla}

\begin{frame}
\vspace{1.0cm}
	\begin{center}Questions?\end{center}
\end{frame}
\note{bla}

### 2015-03-12 test.tex
moved floating point calculation from latex to java because of performance reasons.

\begin{document}
\maketitle
\begin{wrapfigure}{r}{0.47\textwidth}
{ \centering %
\lineChart[width=0.4\textwidth, height=0.3\textwidth, xunit=Money (in €), yunit=Date, options={"title": "Title", "titleHeight": 25}]{SELECT * FROM data1;}%
\\ }
\vspace{-5pt}
\caption{Graph1}
\vspace{-20pt}
\end{wrapfigure} ~\\
Test Queries:\\[3pt]
\sql{SELECT * FROM test;}{SELECT * FROM test;}\\[3pt]
\sql{SELECT col2 FROM test WHERE col1=1;}{SELECT col2 FROM test WHERE col1=1;}\\[3pt]
\sql{INSERT INTO test}{INSERT INTO test VALUES (1, 123);}\\
\sql{VALUES (1, 123);}{INSERT INTO test VALUES (1, 123);}\\[8pt]
Lorem ipsum \sql{SELECT * FROM test;}{SELECT * FROM test;} dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.\\

>>>>

\begin{document}
\maketitle
\begin{wrapfigure}{r}{0.47\textwidth}
{ \centering %
\lineChart[width=0.4\textwidth, height=0.3\textwidth, xunit=Money (in €), yunit=Date, options={"title": "Title", "titleHeight": 25}]{SELECT * FROM data1;}%
\\ }
\vspace{-5pt}
\caption{Graph1}
\vspace{-20pt}
\end{wrapfigure} ~\\
Test Queries:\\[3pt]
\sql{SELECT * FROM test;}\\[3pt]
\sql{SELECT col2 FROM test WHERE col1=1;}\\[3pt]
\sqlmult{INSERT INTO test}{INSERT INTO test VALUES (1, 123);}\\
\sqlmult{VALUES (1, 123);}{INSERT INTO test VALUES (1, 123);}\\[8pt]
Lorem ipsum \sql{SELECT * FROM test;} dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.\\
